\textbf{ Joystream: A Protocol for User Governed Content Platforms }

### 2019-02-25 paper.tex
Grammar tweak

The council for a given term is established through a \textit{council election}, where all members have the opportunity to place weighted backing behind prospective councilors who announce their bid for council membership, and put up their own corresponding stake. The election is conduct towards the end of a term, and current council members are expected to carry out their responsibility of dispatching proposals through their term. The number of council positions in the next term is always set to be a given number in the preceding term, called the \textit{council size}. This may be altered through proposal, and a new number goes into effect at the start of the next term.

>>>>

The council for a given term is established through a \textit{council election}, where all members have the opportunity to place weighted backing behind prospective councilors who announce their bid for council membership, and put up their own corresponding stake. The election is conducted towards the end of a term, and current council members are expected to carry out their responsibility of dispatching proposals through their term. The number of council positions in the next term is always set to be a given number in the preceding term, called the \textit{council size}. This may be altered through a proposal, and a new number goes into effect at the start of the next term.
